---
title: "LxCxUtils_tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LxCxUtils_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
suppressMessages({
  library(LxCxUtils)
  library(Seurat)
  library(SeuratData)
  library(ggplot2)
})
```

# Setup Seurat object

The `LxCxUtils` package mainly uses Seurat objects to get the expression data for the plots, so we first need to setup a Seurat object. We will use the pbmc 3k dataset from the `SeuratData` package.
```{r}
suppressMessages({
  data("pbmc3k")
  pbmc3k
})
```

```{r, echo = FALSE, results='hide'}
pbmc3k <- suppressMessages(UpdateSeuratObject(pbmc3k))
```

```{r}
pbmc3k <- NormalizeData(pbmc3k, verbose = FALSE)
pbmc3k <- FindVariableFeatures(pbmc3k, selection.method = "vst", nfeatures = 2000, verbose = FALSE)
pbmc3k <- ScaleData(pbmc3k, verbose = FALSE)
pbmc3k <- RunPCA(pbmc3k, verbose = FALSE)
```


The first visualisation function from `LxCxUtils` is the `PlotGeneRank`. This function will rank the genes by their expression in each identity of the dataset, and we can even highlight some genes of interest.

```{r}
#highlight no genes
plotGenesRank(pbmc3k, genes_highlight = c())
#highlight some genes
plotGenesRank(pbmc3k, genes_highlight = c("FTL", "LYZ", "MALAT1"))
```
```{r, fig.width=8, fig.asp = 1.8}
#highlight some genes and separate by clusters
plotGenesRank(pbmc3k, genes_highlight = c("FTL", "LYZ", "MALAT1"), group.by = "seurat_annotations")
```

```{r}
QC_barplot(pbmc3k, features = c("nFeature_RNA"))
```





